\chapter{Technologies used and architectural solutions}
\ifpdf
    \graphicspath{{Chapter3/Chapter3Figs/PNG/}{Chapter3/Chapter3Figs/PDF/}{Chapter3/Chapter3Figs/}}
\else
    \graphicspath{{Chapter3/Chapter3Figs/EPS/}{Chapter3/Chapter3Figs/}}
\fi

\section{Environment}
\markboth{\MakeUppercase{\thechapter. Technologies and architecture }}{\thechapter. Technologies used}
It could be stated here that there are many other solutions and the choice was driven by personal experiences and knowledge.

\subsection{Virtual machine served by Vagrant}
What is vagrant? What is it used for? What are boxes? Which box is used?

\subsection{Puppet}
What is puppet?
What are alternatives?
Why is it suitable for a quick deployment of a brand new environment?
What puppet modules are used? \marginnote{PostgreSQL, etc}

\subsection{Python 3}
Small excerpt about Python and its version. 
What programming paradigm is represented by Python?
Why it is recommended to use Python 3.x instead of Python 2.x?

\subsection{Python virtualenv}
What are virtualenvs?
Why is it worthwhile to use it?
How to install all dependencies with one-liner? (pip)

\section{Frameworks and libraries}

\subsection{Django}
What is Django?
What are alternatives in Python? \marginnote{Flask, Pyramid}
What are general alternatives? \marginnote{Java EE, Play! Framework, Ruby on Rails, NodeJS (?)}

\subsection{Django REST Framework}
What is REST?
What does this framework provide?
What are components that should be created to have REST API?
What were the problems with deserialization?

\subsection{Django Allauth}
What is the package used for?
How does OAuth2 work? /marginnote{OAuth2 description might be removed from final version}
How Google Plus authentication may be obtained?
What were obstacles that lead to the decision about not using skills from LinkedIn?

\subsection{Django REST Auth}
Who has made it? What is it used for? Why is it complimentary to the package above?

\subsection{Unittest}
What are unit tests?
Why is it important to write unit tests?
What is tested within this project?

\subsection{Other dependencies}
What can be found in requirements.txt? \marginnote{Optional}

% ------------------------------------------------------------------------


%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../thesis"
%%% End: 
